Shaping strategy in core and flake industry：Standardized manufacturing of QSY (North China) faceted spheroids

### 2025-05-20 analysis/paper/paper.qmd
get the figure showing

ggsave(here("analysis/figures/benn_ternary_plot.jpg"), 
       width = 8, 
       height = 6, 
       dpi = 300)

@@

```{r}
#| label: fig-myfig
#| fig-cap: "the text of the captions. "

knitr::include_graphics(here("analysis/figures/1.png"))
```

@fig-myfig shows...

```{r}
#| label: fig-demo-plot
#| fig-cap: "A plot of random numbers"
plot(rnorm(10))
```

@fig-demo-plot shows how we can have a caption and cross-reference for a plot. Note that figure label and cross-references must both be prefixed with `fig-`

```{r}
#| label: demo-inline-code
#| echo: false
x <- round(pi, 2)
```

Here is an example of inline code `r x` in the middle of a sentence.

>>>>

ggsave(here("analysis/paper/figures/benn_ternary_plot.jpg"), 
       width = 8, 
       height = 6, 
       dpi = 300)

@@

```{r}
#| label: fig-m
#| fig-cap: "the"
#| out-width: "100%"

knitr::include_graphics(here("analysis/paper/figures/1.png"))
```

@fig-m shows...
